Methods for Large Scale Learning to Rank

### 2014-04-07 report/Chapters/CrossBenchmarkComparison.tex
glsdefs in gitignore

Some studies with evaluation results found through in literature review were not usable for the meta-analysis because they 1) used a different evaluation methodology than other studies using the same benchmark \cite{Geng2011, Lin2012}, 2) provided results for different tasks (e.g. rank aggregation or transfer ranking) \cite{De2011, De2010, Derhami2013, Pan2011b, De2012, Chen2010, Ah-Pine2008, Wang2009c, De2013, Miao2013, Hoi2008, De2012b, Duh2011b, Argentini2012, Qin2010c, Volkovs2013, Desarkar2011, Pan2013, Lin2011b, Volkovs2012, Dammak2011}, 3) added additional features to a benchmark dataset \cite{Bidoki2009, Ding2010}, 4) did not provide exact data for evaluation results (often only in graph form) (), 5) reported evaluation results in a different metric than the metrics chosen for this meta-analysis (), 6) reported a higher performance on baseline methods than official runs (), or 7) did not report any baseline performance that allowed us to check validity of the results \cite{Chakrabarti2008, Wang2012b, Buffoni2011}.

>>>>

Some studies with evaluation results found through in literature review were not usable for the meta-analysis because they 1) used a different evaluation methodology than other studies using the same benchmark \cite{Geng2011, Lin2012}, 2) provided results for different tasks (e.g. rank aggregation or transfer ranking) \cite{De2011, De2010, Derhami2013, De2012, Chen2010, Ah-Pine2008, Wang2009c, De2013, Miao2013, Hoi2008, De2012b, Duh2011b, Argentini2012, Qin2010c, Volkovs2013, Desarkar2011, Pan2013, Lin2011b, Volkovs2012, Dammak2011}, 3) added additional features to a benchmark dataset \cite{Bidoki2009, Ding2010}, 4) did not provide exact data for evaluation results (often only in graph form) \cite{Wang2008, Wang2010, Xu2010, Kuo2009, Li2008, Xia2008, Zhou2011, Wu2011, Zhu2009, Karimzadehgan2011, Swersky2012, Pan2011, Ni2008, Ciaramita2008, Stewart2012, Petterson2009, Agarwal2010, Chang2009, Qin2008c, Adams2011, Sculley2009, Huang2008, Alejo2010, Sun2011, He2010b, Benbouzid2012, Geng2012, Chen2012, Xu2012, Shivaswamy2011}, 5) reported evaluation results in a different metric than the metrics chosen for this meta-analysis \cite{Yu2009, Thuy2009, Pahikkala2009, Kersting2009, Mohan2011}, 6) reported a higher performance on baseline methods than official runs \cite{Dubey2009, Banerjee2009, Peng2010b, Song2014, Bian2010, Bian2010b, Carvalho2008, Acharyya2012, Peng2010b, Tran2012, Asadi2013c}, or 7) did not report any baseline performance that allowed us to check validity of the results \cite{Chakrabarti2008, Wang2012b, Buffoni2011}.
